%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {ClearOne Advantage, LLC} % Organization
    {Baltimore, MD} % Location
    {Oct. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{PLACEHOLDER}
        \item {PLACEHOLDER}
        \item {PLACEHOLDER}
        \item {PLACEHOLDER}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Administrator} % Job title
    {ClearOne Advantage, LLC} % Organization
    {Baltimore, MD} % Location
    {Mar. 2018 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managing and monitoring all systems and infrastructure to ensure highest level of availability and reliability.}
        \item {Installing, configuring, testing, and maintaining physical/virtual servers (Microsoft Server 2008, 2012, 2016), application software, etc.}
        \item {Amazon Web Services - EC2 Instance creation, modification, management, and backup. WorkSpaces image creation, bundle creation, and troubleshooting. Route53 DNS host management. Networking changes and maintenance including Security Groups, VPC, Elastic IP's, Gateways, etc.}
        \item {Maintain inContact call flow scripts for IVR and ACD.}
        \item {Redesign and implementation of infrastructure to accomodate for growth from ~150 employees to ~650.}
        \item {Exchange migration of 720 mailboxes from hybrid exchange to Office 365.}
        \item {Telephony/UCaaS redesign and administration, transitioning ~650 users from third party managed phone system to Microsoft Teams.}
        \item {Created scripts (Powershell,Batch,VBScript) and implemented various technologies (WSUS,WDS), providing automation to allow administrative scalability to accommodate for rapid company growth, as well as better end user service without increasing department spend on employee capital.}
        \item {Pandemic Response (COVID-19) - Led TechOps response to pandemic ensuring all on site employees (~450) across two offices were ready to work from home within 48 hours from announcement of physical office closure.}
        \item{Wrote website in PHP on Apache utilizing the S3 facet of Amazon Web Services’ SDK to streamline overall compliance process regarding call recordings, improve data security utilizing presigned URLs, and reduce employee time spent retrieving individual calls from 10-15 minutes to 10 seconds.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Technician} % Job title
    {SCD Information Technology} % Organization
    {Columbia, MD} % Location
    {May 2015 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Appointed senior technician on T\&M contract with property management firm to provide installation and set-up of onsite computers and networks at 200+ sites across the eastern coast of the United States. Interface with security and A/V vendors and integrate their hardware and software into the site setup. Maintain daily contact with the client’s Senior Site Support IT Specialist and the Senior Manager of Information Systems on an as required basis to discuss technical and scheduling issues. Work very closely with client’s internal remote helpdesk staff while onsite to both decrease response and issue resolution time. Increased scope of contract with client to include the management, configuration, and deployment of imaged PC’s via KACE, as well as the configuration and deployment of Meraki security and networking assets to remote sites.}
        \item {Perform onsite and remote support to both SMBs and non-profit organizations. Provide administration and troubleshooting in Windows Server 2008 – 2016 Active Directory, Exchange 2008-2016, Citrix, and VMware ESXi environments.}
        \item {Configure and deploy Dell SonicWALL, Ubiquiti Edgerouter, Cisco Meraki, Sophos UTM, and Barracuda firewalls and network solutions.}
        \item {Responsible for assessing and deploying client needs in terms of network, server, and desktop infrastructure.}
        \item {Responsible for handling Exchange migrations, from onsite to hybrid/full cloud based solution in o365.}
        \item {Responsible for handling various Windows server and domain migrations.}
        \item {Responsible for the migration, deployment, and training of \~160 employees pertaining to the movement of a major Client’s phone system from analogue telephone lines to a hosted VoIP system.}
        \item {Regularly troubleshoot issues pertaining to the termination of Cat5e/6, Coaxial, and Fiber Optic cabling.}
        \item {Conduct and test research on software/hardware solutions, and present information to middle management.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
